\titel

### 2014-03-09 presentation/presa.tex
Planning of nurturing plants
Some history or something
Needs some improvements :)
Explain what MDPs are.
Added the properties of a classical planner vs. MPD
added ff planner and uncertainty

\begin{frame}
  \frametitle{Planning with Uncertainty}
\end{frame}

@@

\begin{frame}
  \frametitle{Planning under uncertainty: FF-Replan}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Uncertainty}

\emph{Uncertainty applies to predictions of future events, to physical measurements that are already made, or to the unknown. Uncertainty arises in partially observable and/or stochastic environments, as well as due to ignorance and/or indolence}

\begin{frame}
  \frametitle{Uncertainty}

Meet my plant

    \includegraphics[scale=0.08]{images/plant.jpg}
\end{frame}

\begin{frame}
  \frametitle{Planning with Uncertainty}

  \begin{columns}
    \column{0.3\textwidth}
    \includegraphics[width=\textwidth]{images/plant.jpg}

    \column{0.7\textwidth}
    How to plan when to water the plant?

    \begin{itemize}
      \item Uncertainty from Wind
      \item Sunlight
      \item Water
    \end{itemize}

  \vspace{1cm}
  What if picking up a block fails?

  \end{columns}
\end{frame}

@@

\begin{frame}
  \frametitle{FF Planner (2001)}

''We have presented an approach to domain independent planning that, \emph{at the time being}, outperforms all existing technology on the majority of the currently available benchmark domains.''

\begin{frame}
  \frametitle{FF Planner (2001)}

Inspired by three new approaches in plan generation during that time:
	\begin{itemize}
		\item Planning graphs
		\begin{itemize}
			\item Nodes are actions and atomic facts arranged into alternate levels
			\item Edges from atomic facts to actions represents conditions
			\item Edges from actions to atomic facts represent true or false 
		\end{itemize}
		\item Planning as a satisfiability method
		\item Heuristic search planning approach
	\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF Planner (2001)}

Relies on a 
	\begin{itemize}
		\item Forward state space search that combines hill-climbing and systematic search
		\item Heuristic estimating goal distances by ignoring delete lists - relaxed GRAPHPLAN
	\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{FF Planner (2001)}

Insert image on search state, enforced hill climbing, call relaxed graphplan, inform search with goal distance estimate and maybe promising succesors, solution plan or fail, possible search from scratch using hast tabel with visited states 
\end{frame}

\begin{frame}
  \frametitle{FF Planner (2001)}
Same image

To avoid wasting time in the presence of goal ordering:
	\begin{itemize}
		\item Goal deletion
		\item Goal agenda techniques
	\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Discussing the FF planner}

Perks
	\begin{itemize}
		\item No efficient algorithmic methods are possible for PSPACE-complete planning, inspired to focus on being efficient on a restricted subclass
		\item Most domains in the IPCC are simple in their structure and can be easily solves using gree algorithms like FF
	\end{itemize}

Criticism
	\begin{itemize}
		\item Methods are motivated by observing example domains - might influence the completeness
		\item Pruning techniques are incomplete
		\item FF behaves poorly in domains with many dead-ends
		\item Solving these tasks with complete best-first search exhaust the memory for larger instances
	\end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Planning under uncertainty: FF-Replan}

  \begin{itemize}
    \item Problem
      \begin{itemize}
        \item MDPs have been the standard for probabilistic planning algorithms
        \item 
      \end{itemize}
  \end{itemize}
